\bf Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-04-22 doc/paper.Rmd
change to ROC curves

```{r}
files <- dir("../data/crossvalidate-cs2/")
cvcs2 <- data.frame()
for (file in files) {
  tmp <- readRDS(file.path("../data/crossvalidate-cs2/",file))
  cvcs2 <- rbind(cvcs2, tmp)
}
cvcs2$coarse <- cvcs2$coarseness
errorsCV <- 
  rbind(errorrate(cvcs2, 0.001), 
        errorrate(cvcs2, 0.005), 
        errorrate(cvcs2, 0.01), 
        errorrate(cvcs2, 0.05))

errorsCV %>% 
  ggplot(aes(x = wo, y = beta)) + 
  geom_point(aes(colour = factor(alpha))) +
  geom_line(aes(colour = factor(alpha))) +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2") +
  scale_shape_discrete(expression("Size of\nvalidation window "~w[v])) +
  xlab(expression("Window size for optimization "~w[o])) +
  ylab("Type II error rate") +
  theme_bw()

>>>>

\autoref{fig:type2} gives an overview of ROC curves for methods CS1 and CS2 over a range of different optimization window sizes $w_o$.

```{r type22, fig.height = 3.5, fig.width = 5, out.width='0.7\\textwidth', fig.cap="ROC curves of methods CS1 and CS2 for different sizes of optimization window $w_o$. Optimal ROC curves are reached at optimization windows of size 150 and higher. Points of equal error rates (EERs) can be found at the intersection of the dotted line and the ROC curves."}
files <- dir("../data/crossvalidate-cs2/")
cvcs2 <- data.frame()
for (file in files) {
  tmp <- readRDS(file.path("../data/crossvalidate-cs2/",file))
  cvcs2 <- rbind(cvcs2, tmp)
}
cvcs2$coarse <- cvcs2$coarseness
library(plotROC)
cvcs2$method <- "CS2"

cvcs2 %>% 
  ggplot(aes(d = as.numeric(!match), m = p_value, colour=factor(wo))) + 
  geom_abline(linetype=3, slope=-1, intercept = 1, colour="grey30", size=.5) +
  geom_roc(labels=FALSE, n.cuts=100, pointsize=0) +
  theme_bw() + 
  scale_colour_brewer(
    expression("Nominal\ntype I error"~alpha), palette="Set2") +
  facet_grid(.~method, labeller="label_both") +
  xlab("False Positives Rate (1 - Specificity)") +
  ylab("True Positives Rate (Sensitivity)")

### 2018-04-22 doc/paper.tex
crossvalidation files
change to ROC curves

\subsection{}\label{section}

>>>>

\subsection{Type II error rates}\label{type-ii-error-rates}

\autoref{fig:type2} gives an overview of ROC curves for methods CS1 and
CS2 over a range of different optimization window sizes \(w_o\).

{\centering \includegraphics[width=0.7\textwidth]{figures/type22-1}

\caption{ROC curves of methods CS1 and CS2 for different sizes of optimization window $w_o$. Optimal ROC curves are reached at optimization windows of size 150 and higher. Points of equal error rates (EERs) can be found at the intersection of the dotted line and the ROC curves.}\label{fig:type22}
\end{figure}
